A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-24 doc/Paper1/ms.tex
Starting to derive covariance matrix

There is a separate $S_i$ parameter $\ell_i$ parameter
for each image; this is because the stellar density and lens convergence is
different at each image position. If the image-specific variability is
predominantly caused by microlensing, the typical timescales and amplitudes
of the microlensing are unlikely to be the same for each image.
In contrast, we use a single $\alpha$ parameter for all images;
this is because it is suspected that the
smoothness of the microlensing variations, which $\alpha$ describes, depends
primarily on the size of the microlensed source, and all images are of the
same source.

The covariance function of the noise-free light curves is then:
\begin{eqnarray}
& & \textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right] \nonumber\\
&=& \left<y_i(t_1)y_j(t_2)\right> \\
&=& \left<\left[f(t_1 - \tau_i) + \mu_i(t_1)\right]\left[f(t_2 - \tau_j) + \mu_j(t_2)\right]\right> \\
&=& \left<f(t_1 - \tau_i)f(t_2 - \tau_j)\right> + \left<\mu_i(t_1)\mu_j(t_2)\right> \\
&=& C_{\rm QSO}(t_1 - \tau_i - t_2 + \tau_j) + \delta_{ij}C_{\rm micro}(t_1 - t_2)
\end{eqnarray}
where the intrinsic variations have been assumed to be uncorrelated with the
microlensing contributions.

>>>>

There is a separate $S_i$ parameter $\ell_i$ parameter
for each image; this is because the stellar density and lens convergence is
different at each image position. If the image-specific variability is
predominantly caused by microlensing, the typical timescales and amplitudes
of the microlensing are unlikely to be the same for each image.
In contrast, we use a single $\alpha$ parameter for all images;
this is because it is suspected that the
smoothness of the microlensing variations, which $\alpha$ describes, depends
primarily on the size of the microlensed source, and all images are of the
same source. We also assume
prior independence of $q(t)$, $\mu_1(t)$, and $\mu_2(t)$.

Recall that the noise-free light curves of the two images are given by:
\begin{eqnarray}
y_1(t) &=& m_1 + q(t) + \mu_1(t) \\
y_2(t) &=& m_2 + q(t - \tau_2) + \mu_2(t) \\
\end{eqnarray}
Using this, and the model assumptions discussed above, we can obtain the
covariance of $y_1$ with itself at a different time, as well as $y_2$ with itself
at a different time and $y_1$ and $y_2$ at any time lag.

\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_j(t_2) - m_j\right)\right]
\end{eqnarray}
where the intrinsic variations have been assumed to be uncorrelated with the
microlensing contributions.
